\lightkurve: an open source Python package for NASA's \kepler, \ktwo~ and \tess~ data analysis

### 2018-05-21 paper/ms.tex
simplify CBV section

\begin{abstract}
The Kepler/K2 mission has provided the astronomy community with light curves of more than 400,000 objects. These ready-made light curves have allowed the community to quickly investigate targets and find exoplanet candidates. However, light curves built by the Kepler pipeline have built-in, fixed assumptions, such as aperture choice and background correction methods. These assumption are valid for the majority of targets, but for certain science cases a bespoke analysis may be needed. Performing custom photometry with the raw Kepler data has many benefits. Working with the raw data allows users to mitigate systematics for their particular science case, (such as the Kepler Rolling band) and verify the aperture selected by the pipeline. Working directly with the pixel data allows users to check the data quality, mitigate and remove cosmic rays or identify stray asteroids in the target aperture. To this end, we present \lightkurve, an open source package for analyzing time-series pixel data using Python. \lightkurve~ is designed to interface seemlessly with data from NASA's \kepler, \ktwo~ and \tess~ missions. Using \lightkurve~ tools it is simple and quick to create corrected time-series photometry from raw pixel data from any of these missions and perform many common light curve corrections, including correcting for K2 motion using the SFF method. \lightkurve~ is open source and provides an excellent learning tool for any users wanting to get to started with Kepler data.

\end{abstract}

@@

For instance, if one assumes that the data comes from an independent and
identically distributed (iid) multivariate Gaussian distribution with mean
$\sum_{j=1}^{n}\theta_j v_{j}(t)$ and known variance $\sigma^2$, then the
cost function can be expressed as follows
\begin{align}
    \mathcal{C}(\bm{\theta}, f_{SAP}) = \sum_{t}\left(f_{SAP}(t)
    - \sum_{j=1}^{n}\theta_j v_{j}(t)\right)^2,
\label{eq:chi-square}
\end{align}
in which $f_{SAP}$ is the SAP flux and $v_j$ is the $j$-th CBV.

The maximum likelihood estimator for $\bm{\theta}$, $\bm{\theta^{\star}}$ can be
expressed as
\begin{align}
    \bm{\theta}^{\star} = \argmin_{\bm{\theta} \in \Theta} \mathcal{C}(\bm{\theta}, f_{SAP}).
\end{align}

However, Equation~(\ref{eq:chi-square}) is sensitive to outliers~\cite{ivezi2014},
therefore, as a default behaviour in \lightkurve, we use the following cost
function
\begin{align}
    \mathcal{C}(\bm{\theta}, f_SAP) = \sum_{t} \left\rvert f_{SAP}(t)
    - \sum_{j=1}^{n}\theta_j v_{j}(t)\right\rvert.
\label{eq:l1-norm}
\end{align}

>>>>

\begin{abstract}
The Kepler/K2 mission has provided the astronomy community with light curves of more than 400,000 objects. These ready-made light curves have allowed the community to quickly investigate targets and find exoplanet candidates. However, light curves built by the Kepler pipeline have built-in, fixed assumptions, such as aperture choice and background correction methods. These assumption are valid for the majority of targets, but for certain science cases a bespoke analysis may be needed. Performing custom photometry with the raw Kepler data has many benefits. Working with the raw data allows users to mitigate systematics for their particular science case, (such as the Kepler Rolling band) and verify the aperture selected by the pipeline. Working directly with the pixel data allows users to check the data quality, mitigate and remove cosmic rays or identify stray asteroids in the target aperture. To this end, we present \lightkurve, an open source package for analyzing time-series pixel data using Python. \lightkurve~ is designed to interface seemlessly with data from NASA's \kepler, \ktwo~ and \tess~ missions. Using \lightkurve~ tools it is simple and quick to create corrected time-series photometry from raw pixel data from any of these missions and perform many common light curve corrections, including correcting for K2 motion using the SFF method. \lightkurve~ is open source and provides an excellent learning tool for any users wanting to get to started with Kepler data.
\end{abstract}

@@

For instance, if one assumes that the data comes from an independent and
identically distributed (iid) multivariate Gaussian distribution with mean
$\sum_{j=1}^{n}\theta_j v_{j}$, in which $v_j$ is the $j$-th CBV, and known
variance $\sigma^2$, then the cost function can be expressed as follows
\begin{align}
    \mathcal{C}(\bm{\theta}, f_{SAP}) = ||f_{SAP} - \bm{\theta}V||^{2}_{2}
\label{eq:chi-square}
\end{align}
in which $f_{SAP}$ is the SAP flux light curve and $V = (v_1, v_2, ..., v_n)^{T}$
is a matrix composed by the CBVs stacked rowwise. The above problem is a simple
linear least-squares problem which presents an analytical solution as
$\theta^{*} = f_{SAP}V^{\mathrm{T}}(VV^{\mathrm{T}})^{-1}$.

However, Equation~(\ref{eq:chi-square}) is sensitive to outliers~\cite{ivezi2014},
therefore, as a default behaviour in \lightkurve, we use the following cost
function
\begin{align}
    \mathcal{C}(\bm{\theta}, f_{SAP}) = \sum_{t} \left\rvert f_{SAP}(t)
    - \sum_{j=1}^{n}\theta_j v_{j}(t)\right\rvert.
\label{eq:l1-norm}
\end{align}
